### 2020-01-14 manuscript/manuscript.rmd
remove some of Nosenko matrices

## The current state of understanding and future direction
Resolving the root position of animal phylogeny that diverged ~ 600 million years ago has proven difficult, even with large genome-scale phylogenomic data matrices. By synthesizing all past phylogenomic studies and perform new analyses to characterize difference between studies, we found the support of Porifera-sister can only be recovered by more complex CAT models with the most closely related outgroups. Three factors contribute significantly to the previous incongruent results. First, the overlap of gene sampling and matrix is extremely low across different studies, leading to the difficult of directly compare the results across different studies. Second, the distribution of phylogenetic signal are largely varied between site-homogeneous and site-heterogeneous models. More importantly, site-heterogeneous models are also more sensitive to outgroup choice than site-homogeneous models, leading to different results even with the same data matrix with different outgoups. Third, we demonstrated that the support of Porifera-sister by data-recoding methods is potentially resulted by data reduction, not accommodation of compositional heterogeneity across species. Thus, the recovery of Porifera-sister needs more constraints than Ctenophora-sister, but that . It is still too early to Rather than embracing one hypothesis over another, our results provide an integrative overview of the challenge and uncertainty related to the origin of animals.

@@

Many key positions of animal phylogeny can be reconstructed by increasing genome-scale data within a phylogenomic framework, although new challenges have also arised. Overcoming the challenges to inferring the earliest diverging animal lineage is particular difficult and here we discuss the several aspects that will help to improve our understanding of animal evolution. First, a broader sampling of high-quality sponge and ctenophore genomes are needed to shorten the long branch since they are among the longest branches in the animal phylogeny (currently only 2 ctenophore and 3 sponge genomes are available). Second, a consensus set of OGs and analytical strages should be generated and fomalized to improve communications and reproducibility of phylogenetic workflow [@guang2016integrated]. Last, we also hope that the work we have conducted here, including consolidating all the datasets in one place with consistent formats and species names, will enhance the technical value of this interesting question to methods-focused investigators that look to develop and evaluate methods or evolutionary models to address this difficult phylogenetic problem. More importantly, we also hope all investigators critically evaluate the competing hypotheses unbiasedly instead of showing preferences to one hypothesis over as a priori due to historical reasons or previous work.

Finally, other sources of evidence may also provide important insight to animal origin, including morphological characters [@mah2014choanoflagellate; @nielsen2019early] and fossil records [@zhao2019cambrian]. We hope the future breakthroughs that will allow us to move the field forward and a consensus viewpoint of early animal evolution will be reached in the coming years.

>>>>

## The current state of understanding and future direction
Resolving the root position of animal phylogeny that diverged ~ 650 million years ago has proven difficult, even with large genome-scale phylogenomic data matrices. By synthesizing all past phylogenomic studies and perform new analyses to characterize difference between studies, we found the support of Porifera-sister can only be recovered by more complex CAT models with the most closely related outgroups, and Ctenophora-sister in all other cases. Three factors contribute significantly to the previous incongruent results. First, the overlap of gene sampling and matrix is extremely low across different studies, leading to the difficult of directly compare the results across different studies. Second, the distribution of phylogenetic signal are largely varied between site-homogeneous and site-heterogeneous models. More importantly, site-heterogeneous models are also more sensitive to outgroup choice than site-homogeneous models, leading to different results even with the same data matrix with different outgoups. Third, we demonstrated that the support of Porifera-sister by data-recoding methods is potentially resulted by data reduction, not accommodation of compositional heterogeneity across species. Thus, the recovery of Porifera-sister needs more constraints than Ctenophora-sister. Rather than embracing one hypothesis over another, our results provide an integrative overview of the challenge and uncertainty related to the origin of animals.

@@

Many key positions of animal phylogeny can be reconstructed by increasing genome-scale data within a phylogenomic framework, although new challenges have also arised. Overcoming the challenges to inferring the earliest diverging animal lineage is particular difficult and here we discuss the several aspects that will help to improve our understanding of animal evolution. First, a broader sampling of high-quality sponge and ctenophore genomes are needed to shorten the long branch since they are among the longest branches in the animal phylogeny (currently only 2 ctenophore and 3 sponge genomes are available). Second, a consensus set of OGs and analytical strateges should be generated and formalized to improve communications and reproducibility of phylogenetic workflow [@guang2016integrated]. Last, we also hope that the work we have conducted here, including consolidating all the datasets in one place with consistent formats and species names, will enhance the technical value of this interesting question to methods-focused investigators that look to develop and evaluate methods or evolutionary models to address this difficult phylogenetic problem. More importantly, we also hope all investigators critically evaluate the competing hypotheses unbiasedly instead of showing preferences to one hypothesis over as a priori due to historical reasons or previous work.Finally, other sources of evidence may also provide important insight to animal origin, including morphological characters [@mah2014choanoflagellate; @nielsen2019early] and fossil records [@zhao2019cambrian]. We hope the future breakthroughs that will allow us to move the field forward and a consensus viewpoint of early animal evolution will be reached in the coming years.
